Dealing with Consumer Uncertainty: Online Consumer Reviews and What makes them helpful?

### 2022-11-05 Paper.Rmd
extend conclusion/EDA

> *"Brief contact with a cockroach will usually render a delicious meal inedible. The inverse phenomenon rendering a pile of cockroaches on a platter edible by contact with one's favorite food-is unheard of. More modestly, consider a dish of a food that you are inclined to dislike: lima beans, fish, or whatever. What could you touch to that food to make it desirable to eat- that is, what is the anti-cockroach? Nothing! And the cockroach is far from unique: there is a wide variety of animals (e.g., worms, caterpillars, slugs, spiders) that share the cockroach potency, along with a variety of microbially or toxin-contaminated objects. One of the best generic descriptions of this relative power of negative contamination is embedded in an age old Russian adage: 'A spoonful of tar can spoil a barrel of honey, but a spoonful of honey does nothing for a barrel of tar.'"*

@@

The ratio of helpfulness is derived from the formula above. Below on Figure \@ref(fig:IV-Hist-Search) the distribution of the helpfulness for search goods can be observed.

@@

@@

The exponential-like distribution of the number of words can be observed for both good types on Figure \@ref(fig:Search-Length) (A) and Figure \@ref(fig:Experience-Length) (A). This means that reviews become less prevalent as they get longer. This might suggest logarithmic transformation can increase the model fit. For the transformed distributions see Figure \@ref(fig:Search-Length) (B) and Figure \@ref(fig:Experience-Length) (B).

@@

Distributions of both product types resemble exponential distribution (see Figure \@ref(fig:Search-Freshness) (A) and Figure \@ref(fig:Experience-Freshness) (A)). Again a logarithmic transformation might be useful here (see Figure \@ref(fig:Search-Freshness) (B) and Figure \@ref(fig:Experience-Freshness) (B)) . Interestingly, even after 3 years from the release date some products are still getting reviewed from customers.

@@

On Figure \@ref(fig:Search-Neg) (A) and Figure \@ref(fig:Experience-Neg) (A) the distributions of the variable for both good types can be seen. On plots, X-axis labels were given in the logarithm of base 10 so 1.00 on the X-axis implies that 10% of the review was negative words. It should be noted that `r round(mean(search_goods$negative == 0), digits = 2)` percent of the reviews for search goods do not have any negative words in them. For experience goods this number is `r round(mean(movies_data$negative == 0), digits = 2)` percent.

@@

This variable was engineered in the same manner with its negative words counterpart. In this case, however, reviews of both good types have more positive words in them proportionally when compared to negative words. `r round(mean(search_goods$positive == 0), digits = 2)` percent of the reviews of search goods do not have any positive words in them and this number is only `r round(mean(movies_data$positive == 0), digits = 2)` for experience goods. Except for zero values both distributions are looking quite normal (see Figure \@ref(fig:Search-Pos) (A) and Figure \@ref(fig:Experience-Pos) (A)).

@@

This study collected Online Consumer Reviews data from two different sources (IMDB and BestBuy) and analyzed the data within the context of consumer uncertainty. Negativity Bias Theorem, Prospect Theory and Search / Experience goods paradigm from information economics were used as theoretical engines to explain the information gathering process of an average consumer. Results showed similarities from the existing Review Helpfulness literature. However, once again it should be noted that the literature has many conflicting results.

This study contributes to the literature as an additional empirical work with a unique BestBuy review data and a unique combination of movie reviews from IMDB. In addition, to my knowledge, this the first study which analyzed the linear interaction between Review Length and Review Rating in terms of Negativity Bias Theorem.

@@

>>>>

> *"Brief contact with a cockroach will usually render a delicious meal inedible. The inverse phenomenon rendering a pile of cockroaches on a platter edible by contact with one's favorite food is unheard of. More modestly, consider a dish of a food that you are inclined to dislike: lima beans, fish, or whatever. What could you touch to that food to make it desirable to eat that is, what is the anti-cockroach? Nothing! And the cockroach is far from unique: there is a wide variety of animals (e.g., worms, caterpillars, slugs, spiders) that share the cockroach potency, along with a variety of microbially or toxin-contaminated objects. One of the best generic descriptions of this relative power of negative contamination is embedded in an age old Russian adage: 'A spoonful of tar can spoil a barrel of honey, but a spoonful of honey does nothing for a barrel of tar.'"*

@@

The ratio of helpfulness is derived from the formula above. Below on Figure \@ref(fig:IV-Hist-Search) the distribution of the helpfulness for search goods can be observed along with the sample mean value which is represented as a vertical line.

@@

Black vertical lines show the mean ratings for both product types. It is nice to see that averages are close to the neutral rating of 3. With this it can be made sure that reviews do not appeal to positive or negative side only.

@@

The exponential-like distribution of the number of words can be observed for both good types on Figure \@ref(fig:Search-Length) (A) and Figure \@ref(fig:Experience-Length) (A). This means that reviews become less prevalent as they get longer. This might suggest logarithmic transformation can increase the model fit. For the transformed distributions see Figure \@ref(fig:Search-Length) (B) and Figure \@ref(fig:Experience-Length) (B). As it can be observed from the vertical mean lines the reviews of the experience goods tend to be longer than the reviews of the search goods.

@@

Distributions of both product types resemble exponential distribution (see Figure \@ref(fig:Search-Freshness) (A) and Figure \@ref(fig:Experience-Freshness) (A)). Again a logarithmic transformation might be useful here (see Figure \@ref(fig:Search-Freshness) (B) and Figure \@ref(fig:Experience-Freshness) (B)) . Interestingly, even after 3 years from the release date some products are still getting reviewed from customers. Vertical mean lines indicate that the products in the experience goods sample are older than the products in the search goods sample because the margin between the first review for a given product and last review for a given product is wider.

@@

On Figure \@ref(fig:Search-Neg) (A) and Figure \@ref(fig:Experience-Neg) (A) the distributions of the variable for both good types can be seen. On plots, X-axis labels were given in the logarithm of base 10 so 1.00 on the X-axis implies that 10% of the review was negative words. For example in this case the mean negative proportion rate is 2,3% ($10^{0.37}$) for search goods and 3,7% ($10^{0.57}$) for experience goods. It should be noted that `r round(mean(search_goods$negative == 0), digits = 2)` percent of the reviews for search goods do not have any negative words in them. For experience goods this number is `r round(mean(movies_data$negative == 0), digits = 2)` percent.

@@

This variable was engineered in the same manner with its negative words counterpart. In this case, however, reviews of both good types have more positive words in them proportionally when compared to negative words. `r round(mean(search_goods$positive == 0), digits = 2)` percent of the reviews of search goods do not have any positive words in them and this number is only `r round(mean(movies_data$positive == 0), digits = 2)` for experience goods. Mean proportion values are 4,4% ($10^{0.64}$) and 5,2% ($10^{0.72}$) for search and experience goods respectively. Except for zero values both distributions are looking quite normal (see Figure \@ref(fig:Search-Pos) (A) and Figure \@ref(fig:Experience-Pos) (A)).

@@

Online Consumer Reviews data were collected from two different sources (IMDB and BestBuy) and analyzed the data within the context of consumer uncertainty in this study. Negativity Bias Theorem, Prospect Theory and Search / Experience goods paradigm from information economics were used as theoretical engines to explain the information gathering process of an average consumer. Results showed similarities from the existing Review Helpfulness literature. However, once again it should be noted that the literature has many conflicting results.

This study contributes to the literature as an additional empirical work with a unique BestBuy review data and a unique combination of movie reviews from IMDB. In addition, to my knowledge, this the first study which analyzed the linear continuous interaction between Review Length and Review Rating in terms of Negativity Bias Theorem. Additionally, there is a lack of emphasis on the sentiment analysis in the existing literature. By employing positive and negative sentiments in terms of Negativity Bias and Prospect Theory this study shows the viability of the sentiment analysis in this context.

@@

Findings show the importance of information sharing for an average online consumer at least for the search goods. Since helpful reviews aid consumers deal with their uncertainty by helping them acquire information concerning the quality of a given product, attendance to information sharing either by writing reviews or voting if the reviews are helpful or not is strongly advised. Search goods results at Table \@ref(tab:Reg-Results-Tobit) can be used as a guide for writing a review. The guidelines can be listed such as this:

1.  Reviewers should only write a review when their opinions of a given product is rather extreme.
2.  Reviewers should share all the information and the experience they accumulated about the product without making it too long because it was observed that helpfulness shows diminishing returns to additional words. The review should be clear and to the point.
3.  Reviewers should not refrain from using negative words as long as it objectively identifies something wrong with the given product.
4.  When reviewers are reviewing a product which they are extremely unhappy about they should give more details and elaborate, on the opposite, when they are content they should write relatively shorter reviews.
5.  Since recent reviews were found to be more helpful on the average, sharing updated information, i.e, writing new reviews is important and encouraged.

With this way consumers would be able to purchase the best good available in the market with respect to their budgets, i.e., maximizing their utilities. This collective behavior may even impact social welfare positively since economic agents are making much more informed decisions. Unfortunately, similar implications can not be made for experience goods, specifically for movies, since the realized results were mostly different that what was hypothesized. Thus, this study can not offer any suggestions for movie reviews.
